Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars

### 2018-07-11 main.tex
Final changes to paper and figures EXCEPT the radiation comparison section

However, much of this work has been done with Lagrangian smoothed particle hydrodynamics schemes, with a few recent exceptions  \citep{Few2012,Simpson2013,Few2014,Vorobyov2015,Corlies2018}. In its original form, this scheme does not capture mixing between chemically inhomogeneous particles, as necessary for chemical evolution. This can be modeled with sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010,Shen2013,Brook2014,Su2017a,Escala2018}, but there are many possibly models that are not necessarily applicable in every regime \citep[see ][]{Revaz2016}. While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing, requiring very high resolution to reduce. Molecular diffusion or even turbulent mixing is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}. Moreover, metal mixing efficiencies may vary species-by-species \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017b}. Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) that inject metals into different phases of 
the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however. The variations in how different methods handle sub-grid metal injection and metal mixing schemes can lead to uncertainties in connecting models to observations and the fundamental physics that drives galaxy evolution.

Increasing physical resolution reduces reliance on sub-grid physics for mixing.  However, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations lose validity  \citep[as studied in detail by][]{Revaz2016}. Below 10$^4$ M$_{\odot}$, such schemes do not fully sample the initial mass function (IMF), and cannot be considered average representations of stellar populations. \textbf{This is acutely problematic at low star formation rate densities with star particle masses comparable to or below the mass of the most massive individual star ($\sim 100$ M$_{\odot}$). At high star formation rate densities, an undersampled IMF in a single low mass star particle can be ompensated for by having many adjacent star particles.} Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2017b}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}. The most straightforward solution is to remove the single stellar population formalism entirely and simply track stars as individual particles.

@@

Using star-by-star modeling, we capture in more detail the stellar yields from individual stars released over their lifetime. This includes yields from massive and AGB stellar winds, and supernovae (SNe). In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars. This ability opens an exciting new channel for testing models of galaxy evolution by leveraging current and ongoing observations probing the detailed distributions of chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}. This paper is the first in a series examining in detail the role that the individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution. We describe each mode of our multi-channel feedback 
in detail in Section~\ref{sec:methods}, describe their implementation in an isolated dwarf galaxy simulation in Section~\ref{sec:IC}, show results from this simulation in Section~\ref{sec:results}, discuss the results in Section~\ref{sec:discussion}, and conclude in Section~\ref{sec:conclusion}.

@@

We use the adaptive mesh refinement hydrodynamics and N-body code \texttt{Enzo}\footnote{http://www.enzo-project.org} to simulate the chemodynamical evolution and detailed feedback physics in a set of high resolution, isolated, low-mass dwarf galaxies. \texttt{Enzo} is an open-source code that is undergoing continual, active development by many researchers across several institutions. We use a substantially modified version of the current development version of \texttt{Enzo} (version 2.X) in this work.\footnote{This version is contained in a publicly available fork of the main repository: https://bitbucket.org/aemerick/enzo-emerick. Specifically, simulations presented here were conducted at changeset 5cc7cea.} We solve the equations of hydrodynamics using a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive Riemann solvers in the event that higher order methods produce negative densities or energies. We compute the total gravitational potential from gas self-gravity, stars, and a static background dark matter potential (see Section~\ref{sec:IC}). Self-gravity is computed with a multigrid Poisson solver. The collisionless star particles are evolved with an adaptive particle-mesh N-body solver at an effective force resolution of $\sim 2 \Delta x$, where $\Delta x$ is the local cell size.

@@

@@

We use the chemistry and cooling library \texttt{Grackle}\footnote{https://grackle.readthedocs.io/en/grackle-3.0/} v 3.0 to follow a nine species non-equilibrium chemistry network (H, H$^+$, He, He$^+$, He$^{++}$, e$^{-}$, H$_2$, H$^{-}$, and H$_{2}$) which includes radiative heating and cooling from these species and metals.\footnote{We use a slightly modified version of the the main \texttt{Grackle} repository, available at https://bitbucket.org/aemerick/grackle-emerick at changeset 59adc76b3130.} \texttt{Grackle} is a freely available, open source, multi-code library, designed to interface with a wide variety of astrophysical codes. We outline specific model choices made in our simulations and refer the reader to \citet{GrackleMethod} for a detailed discussion of the code. We apply the \citet{Glover2008} three-body rate for H$_{2}$ formation and include a model for H$_2$ formation on dust, dust heating, and dust cooling following the methods in \citet{2000ApJ...534..809O} and \citet{2005ApJ...626..627O} as included in \texttt{Grackle}. However, we update the default dust to gas ratio scaling in \texttt{Grackle} to account for the steeper scaling in low metallicity regimes ($Z \lesssim 0.1 Z_{\odot}$), using the broken power law scalings from \citet{Remy-Ruyer2014}. For metallicities above $\sim 0.1 Z_{\odot}$, this is equivalent to the default behavior of \texttt{Grackle}, where dust content scales linearly with metallicity.
% Since we assume a dust abundance that depends only on metallicity, we do not track dust destruction or creation, which may play an important role regulating detailed ISM properties. (Vogelsberger is working on this directly but no papers yet... will cite if it gets submitted by then)

@@

Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low-metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy \citep{Simpson2013}. We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for HI self-shielding against the UV background \citep[see][ for more details of this implementation]{GrackleMethod}. We assume HeI ionization generally follows HI. This allows us to approximate HeI self-shielding using the same form (A. Rahmati, private communication). We ignore HeII photoionization from the UV background entirely. {\bf For consistency, we additionally reduce the reaction rates for direct H$_2$ ionization (, eV) and H$_2^+$ destruction (,eV) by the same shielding factors computed for HI and HeI shielding.}\footnote{Ignoring this effect leads to unrealistically high electron fractions in self-shielding gas from direct $H_2$ ionization, which drives significant production of H$_2$ via gas-phase reactions.} Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from \textsc{Cloudy} (see Section 4.1.1 of \citet{Hu2017}). As mentioned previously, we have re-computed metal line cooling tables using \textsc{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription. This is described in more detail in Appendix ~\ref{appendix:cooling}.

@@

The galaxy initially consists of a smooth, exponential gas disk in hydrostatic equilibrium with a static, background dark matter potential. The gas profile follows \citet{Tonnesen2009} and \citet{Salem2015}, with
\begin{equation}
\rho_{\rm gas} (R,z) = \frac{M_{\rm o}}{2\pi a^2_{\rm gas}b_{\rm gas}} 0.5^2{\rm sech}\left(\frac{R}{a_{\rm gas}}\right){\rm sech}\left(\frac{z}{b_{\rm gas}}\right)
\end{equation}
where $a_{\rm gas}$ and $b_{\rm gas}$ are the radial and vertical gas disk scale heights, and $M_{\rm o}$ is approximately 70\% of the total gas mass. We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and $M_o = 1.26\times 10^6$~M$_{\odot}$. We adopt a \citet{Burkert1995} dark matter potential with \textbf{virial mass and radius} $M_{\rm vir} = 2.48\times 10^{9}~M_{\odot}$ and $R_{\rm vir}~=~27.4$~kpc as defined in \citep{BryanNorman1998} and \textbf{scale radius} r$_{\rm s} = 990$~pc. This gives a maximum circular velocity $V_{\rm max} = 30.1$~km~s$^{-1}$ at $R_{\rm vmax}~=~3.2$~kpc. These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc of $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties within the halo mass expected for galaxies of this size \citep{Ferrero2012,Read2017}. We will explore the effect of adopting different dark matter potentials within the large range of possible profiles in future work.

Following the initialization procedure of \citet{Hu2017}, we use artificial SN driving to generate realistic initial densities and turbulent properties in the galaxy ISM. This prevents an otherwise uniform collapse of the gas disk at the beginning of the simulation. During this period, SNe explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central HI surface density and the relation presented in \citep{Roychowdhury2009}. We stop the artificial driving 25~Myr after the first star particle forms. These artificial SNe do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances. We note that this initial driving is somewhat ad hoc in that we do not include any other effects from the stellar population that would have caused these SNe.

We emphasize here that our model, with no initial stellar distribution, is not intended to reproduce the evolution of Leo P, which has formed stars continuously over cosmological timescales. In addition, the mass fractions for the individual metals we track are set to zero so that we follow only the evolution of metals self-consistently produced in the simulations. Otherwise, the galaxy chemical properties would be dominated by the somewhat arbitrary choice of initial abundances. In some ways this is similar to the first pollution of pristine gas in the early Universe, but we note that we cannot directly make this comparison as the environmental conditions and UVB properties were different at high redshift, and we explicitly ignore Pop III and Pop II stellar evolution. Instead, this work is intended as a numerical experiment to investigate how metal enrichment from ongoing star formation proceeds in a gas / dark matter environment similar to low mass halos at both low redshift and the early Universe. The subsequent metal enrichment from the stars in our simulation can be thought of as tracking 
a change in abundances from arbitrary initial conditions. We will discuss how to make proper comparisons to observed stellar and gas abundance properties of dwarf galaxies in future work, where we will investigate the abundance evolution of our simulations in more detail.

\section{Results}
\label{sec:results}
We present our initial results here, providing an overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the 500~Myr after the first new star forms. Unless otherwise noted, $t = 0$ is defined as the time at which that first star particle forms, which is 43~Myr after the actual beginning of the simulation run. The galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and vertical heigh $|z| < 200$~pc relative to the center of the galaxy. ISM properties are calculated considering only the gas contained within the disk of the galaxy. We include a resolution study in Appendix \ref{appendix:resolution_study}.

Our analysis makes extensive use of the open-source \textsc{yt} toolkit \citep{yt}. All analysis scripts used in this work can be found at https://github.com/aemerick/galaxy-analysis at changeset 66452ba.

@@

The initially puffy gas distribution collapses to a thin disk, with scale heights between 10--30~pc, as shown by the blue line in Fig~\ref{fig:scale_height}. This figure shows the scale height of all gas in the disk, averaged over 40~Myr periods centered on each given time. Stellar feedback acts to heat up this initially thin disk substantially, creating typical scale heights of 50--200~pc. Towards the end of the simulation time, the half-light radius is $390 \pm 21$ pc, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr. Although the disk remains thin beyond the half-light radius, with a scale height of around 40--60~pc, it is fully resolved at all radii. By the end of the simulation, the majority of the gas has a scale height of $\sim$100~pc.

Constraining the gas scale height in ultra-faint dwarf galaxies observationally, to compare to our simulations, is challenging. For Leo P, located at 1.7~Mpc, HI observations that are capable of detecting the diffuse HI throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest HI clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.

@@

Interestingly, there is significant structure well above the gas disk in our model, in the form of dense clouds and filamentary features, as seen in the edge-on projections. These cold gas clumps appear to have typical sizes on order of $\sim 10$~pc, but with lower density tails that can extend up to 100 pc. These consist of both cool, self-gravitating gas clumps that are being pushed out and ablated by the stellar feedback driven winds, and gas that is cooling and condensing in the disk-halo interface of our dwarf galaxy. These clumps have typical velocities on order of a few to tens of kilometers per second, and appear to survive for 10--100 Myr before being fully ablated or re-accreted onto the main body of the gaseous disk. The evolution of these dense clumps in the context of the disk-halo interface in our low mass dwarf galaxy will be examined in a future work. 
% AE (left out): This is exciting given recent \citep[e.g.][]{Zheng2017} and ongoing \citep{Zheng2017HST} observational observational work examining the disk-halo interface in nearby galaxies.

@@

At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component. By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, \textbf{ with a molecular hydrogen mass fraction of only $\sim$ 0.3 \%. The molecular component declines rapidly as this gas is both converted into stars and is destroyed by stellar radiation feedback. For the remainder of the simulation, the H$_2$ mass generally increases,  with small fluctuations during periods of star formation, reaching a peak mass fraction of 5\% by the end of the simulation. The growth of the molecular fraction is due in part to a decline in the total gas content of our galaxy due to feedback-driven galactic winds. During these outflows, the densest gas, the molecular gas, is preferentially retained over the more diffuse ISM. Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}. The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.}

@@

Our simulations include sufficient resolution and microphysics to capture a multi-phase medium within the ISM and halo of our simulated galaxy. We define five different gas phases following those defined in \citep{Draine2011}: molecular gas, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM). We emphasize that the molecular ISM phase is defined as all cells with M$_{\rm H_2}$/M$_{\rm gas} = $~f$_{\rm H_2} > 0.5$, and is thus somewhat different than simply considering the total H$_2$ content. \textbf{We further note that no region in our galaxy is more than 0.5\% molecular}. See Appendix \ref{appendix:phases} for a quantitative definition of these phases. These presence of phases are regulated by the complex interplay between cooling, turbulence, self-gravity, and radiative and shock heating from stellar feedback throughout the galaxy's evolution. Here we discuss the thermodynamic properties of the gas within the inner halo of our dwarf galaxy.

>>>>

However, much of this work has been done with Lagrangian smoothed particle hydrodynamics schemes, with a few recent exceptions  \citep{Few2012,Simpson2013,Few2014,Vorobyov2015,Corlies2018}. In its original form, this scheme does not capture mixing between chemically inhomogeneous particles, as necessary for chemical evolution. This can be modeled with sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010,Shen2013,Brook2014,Su2017a,Escala2018}, but there are many possible models and each is not necessarily applicable in every regime \citep[see ][]{Revaz2016}. While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing in simulations without sufficienty high spatial resolution. Molecular diffusion or even turbulent mixing is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}. Moreover, metal mixing efficiencies may vary species-by-species \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017b, KrumholzTing2018}. Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) that inject metals into different phases of 
the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however. The variations in how different methods handle sub-grid metal injection and metal mixing schemes can lead to uncertainties in connecting models to observations and the fundamental physics that drives galaxy evolution.

Increasing physical resolution reduces reliance on sub-grid physics for mixing.  However, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations lose validity  \citep[as studied in detail by][]{Revaz2016}. Below 10$^4$ M$_{\odot}$, such schemes do not fully sample the initial mass function (IMF), and cannot be considered average representations of stellar populations. \textbf{This is acutely problematic at low star formation rate densities with star particle masses comparable to or below the mass of the most massive individual star ($\sim 100$ M$_{\odot}$). At high star formation rate densities, an undersampled IMF in a single low mass star particle can be compensated for by having many adjacent star particles.} Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2017b}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}. The most straightforward solution is to remove the single stellar population formalism entirely and simply track stars as individual particles.

@@

Using star-by-star modeling, we capture in more detail the stellar yields from individual stars released over their lifetime. This includes yields from massive and AGB stellar winds, and supernovae (SNe). In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars. This ability opens an exciting new channel for testing models of galaxy evolution by leveraging current and ongoing observations probing the detailed distributions of chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}. This paper is the first in a series examining in detail the role that individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution. We describe each mode of our multi-channel feedback 
in detail in Section~\ref{sec:methods}, describe their implementation in an isolated dwarf galaxy simulation in Section~\ref{sec:IC}, show results from this simulation in Section~\ref{sec:results}, discuss the results in Section~\ref{sec:discussion}, and conclude in Section~\ref{sec:conclusion}.

@@

We use the adaptive mesh refinement hydrodynamics and N-body code \texttt{Enzo}\footnote{http://www.enzo-project.org} to simulate the chemodynamical evolution and detailed feedback physics in a set of high resolution, isolated, low-mass dwarf galaxies. \texttt{Enzo} is an open-source code that is undergoing continual, active development by many researchers across several institutions. We use a substantially modified version of the current development version of \texttt{Enzo} (version 2.X) in this work.\footnote{This version is contained in a publicly available fork of the main repository: https://bitbucket.org/aemerick/enzo-emerick. Specifically, simulations presented here were conducted at changeset 7001d99.} We solve the equations of hydrodynamics using a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive Riemann solvers in the event that higher order methods produce negative densities or energies. We compute the total gravitational potential from gas self-gravity, stars, and a static background dark matter potential (see Section~\ref{sec:IC}). Self-gravity is computed with a multigrid Poisson solver. The collisionless star particles are evolved with an adaptive particle-mesh N-body solver at an effective force resolution of $\sim 2 \Delta x$, where $\Delta x$ is the local cell size.

@@

\textbf{Due to computational constraints we found it necessary to institute a temperature ceiling in low density, diffuse gas. These high temperatures, typically well above 10$^{7}$~K and up to 10$^{8}$~K, would place an onerous constraint on the limiting time step at high spatial resolution. At these temperatures, with typical velocities up to $\sim$10$^{3}$~km~s$^{-1}$, satisfying the Courant condition requires time steps on order of 100~yr. We institute a maximum temperature of 8$\times 10^6$~K in gas with densities between 10$^{-30}$~g~cm$^{-3}$ and 10$^{-26}$~g~cm$^{-3}$. These densities were somewhat arbitrarily chosen, but ensure that this threshold does not impact very low density gas in the halo of our dwarf galaxy or higher density gas in supernova injection regions. This threshold decreases the required run-time by factors of a few. The value of the temperature threshold was chosen to ensure the affected hot gas remained just above the high-temperature minimum of our cooling curve (see Appendix~\ref{appendix:cooling}.)}

@@

We use the chemistry and cooling library \texttt{Grackle}\footnote{https://grackle.readthedocs.io/en/grackle-3.0/} v 3.0 to follow a nine species non-equilibrium chemistry network (H, H$^+$, He, He$^+$, He$^{++}$, e$^{-}$, H$_2$, H$^{-}$, and H$_{2}$) which includes radiative heating and cooling from these species and metals.\footnote{We use a slightly modified version of the the main \texttt{Grackle} repository, available at https://bitbucket.org/aemerick/grackle-emerick at changeset c2c0faf.} \texttt{Grackle} is a freely available, open source, multi-code library, designed to interface with a wide variety of astrophysical codes. We outline specific model choices made in our simulations and refer the reader to \citet{GrackleMethod} for a detailed discussion of the code. We apply the \citet{Glover2008} three-body rate for H$_{2}$ formation and include a model for H$_2$ formation on dust, dust heating, and dust cooling following the methods in \citet{2000ApJ...534..809O} and \citet{2005ApJ...626..627O} as included in \texttt{Grackle}. However, we update the default dust to gas ratio scaling in \texttt{Grackle} to account for the steeper scaling in low metallicity regimes ($Z \lesssim 0.1 Z_{\odot}$), using the broken power law scalings from \citet{Remy-Ruyer2014}. For metallicities above $\sim 0.1 Z_{\odot}$, this is equivalent to the default behavior of \texttt{Grackle}, where dust content scales linearly with metallicity.
% Since we assume a dust abundance that depends only on metallicity, we do not track dust destruction or creation, which may play an important role regulating detailed ISM properties. (Vogelsberger is working on this directly but no papers yet... will cite if it gets submitted by then)

@@

Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low-metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy \citep{Simpson2013}. We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for HI self-shielding against the UV background \citep[see][ for more details of this implementation]{GrackleMethod}. We assume HeI ionization generally follows HI. This allows us to approximate HeI self-shielding using the same form (A. Rahmati, private communication). We ignore HeII photoionization from the UV background entirely. {\bf For consistency, we additionally reduce the reaction rates for direct H$_2$ ionization (15.4 eV) and H$_2^+$ destruction (30 eV) by the same shielding factors computed for HI and HeI shielding.}\footnote{Ignoring this effect leads to unrealistically high electron fractions in self-shielding gas from direct $H_2$ ionization, which drives significant production of H$_2$ via gas-phase reactions.} Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from \textsc{Cloudy} (see Section 4.1.1 of \citet{Hu2017}). As mentioned previously, we have re-computed metal line cooling tables using \textsc{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription. This is described in more detail in Appendix ~\ref{appendix:cooling}.

@@

The galaxy initially consists of a smooth, exponential gas disk in hydrostatic equilibrium with a static, background dark matter potential. The gas profile follows \citet{Tonnesen2009} and \citet{Salem2015}, with
\begin{equation}
\rho_{\rm gas} (R,z) = \frac{M_{\rm o}}{2\pi a^2_{\rm gas}b_{\rm gas}} 0.5^2{\rm sech}\left(\frac{R}{a_{\rm gas}}\right){\rm sech}\left(\frac{z}{b_{\rm gas}}\right)
\end{equation}
where $a_{\rm gas}$ and $b_{\rm gas}$ are the radial and vertical gas disk scale heights, and $M_{\rm o}$ is approximately 70\% of the total gas mass. We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and $M_o = 1.26\times 10^6$~M$_{\odot}$. We adopt a \citet{Burkert1995} dark matter potential with \textbf{virial mass and radius} $M_{\rm vir} = 2.48\times 10^{9}~M_{\odot}$ and $R_{\rm vir}~=~27.4$~kpc as defined in \citep{BryanNorman1998} and \textbf{scale radius} r$_{\rm s} = 990$~pc. This gives a maximum circular velocity $V_{\rm max} = 30.1$~km~s$^{-1}$ at $R_{\rm vmax}~=~3.2$~kpc. These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc of $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties within the halo mass expected for galaxies of this size \citep{Ferrero2012,Read2017}.

% AE: removing this as it may no longer be the case
%We will explore the effect of adopting different dark matter potentials within the large range of possible profiles in future work.

Following the initialization procedure of \citet{Hu2017}, we use artificial SN driving to generate realistic initial densities and turbulent properties in the galaxy ISM. This prevents an otherwise uniform collapse of the gas disk at the beginning of the simulation. During this period, SNe explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central HI surface density and the relation presented in \citep{Roychowdhury2009}. We stop the artificial driving 25~Myr after the first star particle forms. These artificial SNe do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances. We note this initial driving is ad hoc in that we do not include other effects from the stellar population that would have caused these SNe.

We emphasize here that our model, with no initial stellar distribution, is not intended to identically reproduce the evolution of Leo P, which has formed stars continuously over cosmological timescales. In addition, the mass fractions for the individual metals we track are set to zero so that we follow only the evolution of metals self-consistently produced in the simulations. Otherwise, the galaxy chemical properties would be dominated by the somewhat arbitrary choice of initial abundances. In some ways this is similar to the first pollution of pristine gas in the early Universe, but we note that we cannot directly make this comparison as the environmental conditions and UVB properties were different at high redshift, and we explicitly ignore Pop III and Pop II stellar evolution. Instead, this work is intended as a numerical experiment to investigate how metal enrichment from ongoing star formation proceeds in a gas / dark matter environment similar to low mass halos at both low redshift and the early Universe. The subsequent metal enrichment from the stars in our simulation can be thought of as tracking 
a change in abundances from arbitrary initial conditions. We will discuss how to make proper comparisons to observed stellar and gas abundance properties of dwarf galaxies in future work, where we will investigate the abundance evolution of our simulations in more detail.

\section{Results}
\label{sec:results}
We present our initial results here, providing an overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the 500~Myr after the first new star forms. Unless otherwise noted, $t = 0$ is defined as the time at which that first star particle forms, which is 43~Myr after the actual beginning of the simulation run. The galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and vertical height $|z| < 200$~pc relative to the center of the galaxy. ISM properties are calculated considering only the gas contained within the disk of the galaxy. We include a resolution study in Appendix \ref{appendix:resolution_study}.

Our analysis makes extensive use of the open-source \textsc{yt} toolkit \citep{yt}. All analysis scripts used in this work can be found at https://github.com/aemerick/galaxy-analysis at changeset dd76ad10.

@@

The initially puffy gas distribution collapses to a thin disk, with scale heights between 10--30~pc, as shown by the blue line in Fig~\ref{fig:scale_height}. This figure shows the scale height of all gas in the disk, averaged over 20~Myr periods centered on each given time. Stellar feedback acts to heat up this initially thin disk substantially, creating typical scale heights of 50--120~pc. Towards the end of the simulation time, the half-light radius is $391 \pm 19$ pc, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr. Although the disk remains thin beyond the half-light radius, with a scale height of around 50~pc, it is fully resolved at all radii. By the end of the simulation, the majority of the disk has a scale height of $\sim$100~pc.

Constraining the gas scale height in ultra-faint dwarf galaxies observationally is challenging. For Leo P, located at 1.7~Mpc, HI observations that are capable of detecting the diffuse HI throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest HI clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}. \textbf{In the final column of Figure~\ref{fig:panel_z}, the peak HI column density reaches $N_{\rm HI} = 9.4 \times 10^{21}$~cm$^{-2}$, but is located in dense regions with sizes $<$ 10$\sim$pc. With a resolution of 100~pc, the peak column density in an edge-on view is $N_{\rm HI} = 4.3 \times 10^{20}$~cm$^{-2}$, and $N_{\rm HI} = 2.8 \times 10^{20}$~cm$^{-2}$ in a face-on view. At 500 pc resolution, this corresponds to $N_{\rm HI} = 7.5 \times 10^{19}$~cm$^{-2}$, and $N_{\rm HI} = 6.2 \times 10^{19}$~cm$^{-2}$. These column densities are consistent with the resolution-dependent peak column densities found in the low mass dwarf galaxy sample of \cite{Teich2016}, and consistent with the observed peak column density of Leo P, $N_{\rm HI} = 6.5 \times 10^{20}$~cm$^{-2}$, observed with a spatial resolution of about 33~pc.}

@@

@@

At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component. By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, \textbf{ with a molecular hydrogen mass fraction of only $\sim$ 0.3 \%. The molecular component declines rapidly as this gas is both converted into stars and is destroyed by stellar radiation feedback. For the remainder of the simulation, the H$_2$ mass generally increases,  with small fluctuations during periods of star formation, reaching a peak mass fraction of 5\% at 500~Myr. The growth of the molecular fraction is due in part to a decline in the total gas content of our galaxy from feedback-driven galactic winds. During these outflows, the densest gas, the molecular gas, is preferentially retained over the more diffuse ISM. Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}. The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.}

@@

Our simulations include sufficient resolution and microphysics to capture a multi-phase medium within the ISM and halo of our simulated galaxy. We define five different gas phases following those defined in \citep{Draine2011}: molecular gas, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM). We emphasize that the molecular ISM phase is defined as all cells with M$_{\rm H_2}$/M$_{\rm gas} = $~f$_{\rm H_2} > 0.5$, and is thus somewhat different than simply considering the total H$_2$ content. \textbf{We further note that no region in our galaxy is more than 50.0\% molecular}. See Appendix \ref{appendix:phases} for a quantitative definition of these phases. The properties of these phases are regulated by the complex interplay between cooling, turbulence, self-gravity, and radiative and shock heating from stellar feedback throughout the galaxy's evolution. Here we discuss the thermodynamic properties of the gas within the inner halo of our dwarf galaxy.

Figure~\ref{fig:phase} shows the temperature-density distribution of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300--350~Myr. One can readily identify the two regimes containing most of the mass in the simulation: low density, warm gas produced through ionization and SN heating, and cold, high density gas that makes up most of the mass in the galaxy's disk (see Figure~\ref{fig:ISM_evolution}). Several notable features of the distribution include: broad ranges of temperature even in quite dense gas, perhaps produced by photoionization and photoelectric heating, a substantial amount of extremely cold gas below 10~K, and the lack of well-defined thermal phases due to the complexity of both the heating and cooling in a turbulent medium. We note that we are likely missing important physics, such as cosmic ray heating and ionization, that would prevent the formation of the coldest gas in this diagram (below about 10~K), but we do not expect this to significantly alter our results. \textbf{Our artificial temperature ceiling in diffuse gas (see Section~\ref{sec:hydro}) is seen clearly by the horizontal feature in the top left.}  The boxed regime in the lower right corner shows our star formation density and temperature threshold. Gas in this regime is rapidly consumed by star formation and subsequent feedback. Given the small size of our dwarf galaxy, the total amount of mass in this regime at any given instant can be small, but does appear in this time average. We will investigate the typical formation and destruction timescales of this dense, star forming gas in future work.
